`r params$doc_title`

### 2023-04-19 scripts/MSc.Rmd
run nsim100 with PRESSO and GENARCH

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "./output/Rdata/sim-results/", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "./output/Rdata/sim-results/", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
nsim_architectures <- nrow(est_sim_architectures[[1]])
```

>>>>

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "./output/Rdata/sim-results/", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "./output/Rdata/sim-results/", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
nsim_architectures <- nrow(est_sim_architectures[[1]])

all(is.na(est_sim$PRESSO_theta_se_sim_BMI_GSD_200000))
all(is.na(est_sim_architectures[[1]]$PRESSO_mr_pval_BMI_GSD_200000))
est_sim_PRESSO <- readRDS("./output/Rdata/_old/2022-12-23_est_sim_NSIM_100.rds")
